---
title: "Data preparation"
bibliography: references.bib
date: "Last compiled on `r format(Sys.time(), '%B, %Y')`"
output: 
  html_document:
    css: tweaks.css
    toc:  true
    toc_float: true
    number_sections: true
    toc_depth: 1
    code_folding: show
    code_download: yes
---

```{r, globalsettings, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
library(knitr)
library(tidyverse)
knitr::opts_chunk$set(echo = TRUE)
opts_chunk$set(tidy.opts=list(width.cutoff=100),tidy=TRUE, warning = FALSE, message = FALSE,comment = "#>", cache=TRUE, class.source=c("test"), class.output=c("test3"))
options(width = 100)
rgl::setupKnitr()

colorize <- function(x, color) {sprintf("<span style='color: %s;'>%s</span>", color, x) }
```


```{r klippy, echo=FALSE, include=TRUE}
klippy::klippy(position = c('top', 'right'))
#klippy::klippy(color = 'darkred')
#klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done')
```


---  


To copy the code, click the button in the upper right corner of the code-chunks.

# Getting started

## clean up

```{r, results='hide'}
rm(list=ls())
gc()
```

<br>

## general custom functions

- `fpackage.check`: Check if packages are installed (and install if not) in R
- `fsave`: Function to save data with time stamp in correct directory
- `fload`: Function to load R-objects under new names
- `fshowdf`: Print objects (`tibble` / `data.frame`) nicely on screen in `.Rmd`
- `ftheme`: pretty ggplot2 theme

```{r, eval=FALSE}
fpackage.check <- function(packages) {
    lapply(packages, FUN = function(x) {
        if (!require(x, character.only = TRUE)) {
            install.packages(x, dependencies = TRUE)
            library(x, character.only = TRUE)
        }
    })
}

fsave <- function(x, file, location = "./data/processed/", ...) {
    if (!dir.exists(location))
        dir.create(location)
    datename <- substr(gsub("[:-]", "", Sys.time()), 1, 8)
    totalname <- paste(location, datename, file, sep = "")
    print(paste("SAVED: ", totalname, sep = ""))
    save(x, file = totalname)
}


fload  <- function(fileName){
  load(fileName)
  get(ls()[ls() != "fileName"])
}


fshowdf <- function(x, ...) {
    knitr::kable(x, digits = 2, "html", ...) %>%
        kableExtra::kable_styling(bootstrap_options = c("striped", "hover")) %>%
        kableExtra::scroll_box(width = "100%", height = "300px")
}

ftheme <- function() {
  #download font at https://fonts.google.com/specimen/Jost/
  theme_minimal(base_family = "Jost") +
    theme(panel.grid.minor = element_blank(),
          plot.title = element_text(family = "Jost", face = "bold"),
          axis.title = element_text(family = "Jost Medium"),
          axis.title.x = element_text(hjust = 0),
          axis.title.y = element_text(hjust = 1),
          strip.text = element_text(family = "Jost", face = "bold",
                                    size = rel(0.75), hjust = 0),
          strip.background = element_rect(fill = "grey90", color = NA),
          legend.position = "bottom")
}
```

```{r fonts, echo=FALSE, warning=FALSE, results='hide', eval=FALSE}
# import font JOST
#extrafont::font_import(pattern = "Jost")
extrafont::loadfonts(device="win")

# Set default theme and font stuff
ggplot2::theme_set(ftheme())
ggplot2::update_geom_defaults("text", list(family = "Jost", fontface = "plain"))
ggplot2::update_geom_defaults("label", list(family = "Jost", fontface = "plain"))
```


<br>

## necessary packages

- `tidyverse`: data wrangling
- `haven`: read and write various data formats
- `sjlabelled`: work with labelled (SPSS) data

```{r, eval=FALSE}
packages = c("tidyverse", "haven", "sjlabelled")
fpackage.check(packages)
rm(packages)
```


<br>


---

# Import data

Import and unlabel wave 3 of the TRIAL survey.

```{r, import, eval=FALSE}
read_sav("./rawdata/DRADTRIAL23_eindbestand.sav") %>%
  sjlabelled::unlabel(., verbose=FALSE) -> df
```

<br> 

# wrangling DCE data

```{r, dcedat, eval=FALSE}
#make respondent id 
df$id <- 1:nrow(df)

#to long format

#each list element contains the choices for each set:
#thus, reistijd.list[[2]][3] is the level of the travel time attribute of person 3 in choice-set 2.

reistijd.list <- list(
  c("Reistijd_A1", "Reistijd_A2"),
  c("Reistijd_B1", "Reistijd_B2"),
  c("Reistijd_C1", "Reistijd_C2")
)

frequentie.list <- list(
  c("Trainningsfrequentie_A1", "Trainningsfrequentie_A2"),
  c("Trainningsfrequentie_B1", "Trainningsfrequentie_B2"),
  c("Trainningsfrequentie_C1", "Trainningsfrequentie_C2")
)

webpagina.list <- list(
  c("Webpagina_A1", "Webpagina_A2"),
  c("Webpagina_B1", "Webpagina_B2"),
  c("Webpagina_C1", "Webpagina_C2")
)

bekenden.list <- list(
  c("Bekenden_A1", "Bekenden_A2"),
  c("Bekenden_B1", "Bekenden_B2"),
  c("Bekenden_C1", "Bekenden_C2")
)

clubopleiding.list  <- list(
  c("Clubleden_opleiding_A1", "Clubleden_opleiding_A2"),
  c("Clubleden_opleiding_B1", "Clubleden_opleiding_B2"),
  c("Clubleden_opleiding_C1", "Clubleden_opleiding_C2")
)

clubmigratie.list  <- list(
  c("Clubleden_migratieachtergrond_A1", "Clubleden_migratieachtergrond_A2"),
  c("Clubleden_migratieachtergrond_B1", "Clubleden_migratieachtergrond_B2"),
  c("Clubleden_migratieachtergrond_C1", "Clubleden_migratieachtergrond_C2")
)

teamopleiding.list  <- list(
  c("Trainingsgroep_opleiding_A1", "Trainingsgroep_opleiding_A2"),
  c("Trainingsgroep_opleiding_B1", "Trainingsgroep_opleiding_B2"),
  c("Trainingsgroep_opleiding_C1", "Trainingsgroep_opleiding_C2")
)

teammigratie.list  <- list(
  c("Trainingsgroep_migratieachtergrond_A1", "Trainingsgroep_migratieachtergrond_A2"),
  c("Trainingsgroep_migratieachtergrond_B1", "Trainingsgroep_migratieachtergrond_B2"),
  c("Trainingsgroep_migratieachtergrond_C1", "Trainingsgroep_migratieachtergrond_C2")
)

chosen <- c("V107_1", "V107_2", "V107_3")

for (set in 1:3) {

  # to long format
  
  for (choice in 1:2) {
    
    data <- as.data.frame(df)
    data$set <- set
    data$options <- choice
    data$traveltime <- data[, names(data) == reistijd.list[[set]][choice]]
    data$trainfreq <- data[, names(data) == frequentie.list[[set]][choice]]
    data$webpage <- data[, names(data) == webpagina.list[[set]][choice]]
    data$acquaintances <- data[, names(data) == bekenden.list[[set]][choice]]
    data$educ_club <- data[, names(data) == clubopleiding.list[[set]][choice]]
    data$educ_team <- data[, names(data) == teamopleiding.list[[set]][choice]]
    data$migrant_club <- data[, names(data) == clubmigratie.list[[set]][choice]]
    data$migrant_team <- data[, names(data) == teammigratie.list[[set]][choice]]
    data$chosen <- data[, names(data) == chosen[set]]
    
    data <- data[, names(data) %in% c("id", "set", "options", "traveltime", "trainfreq", "webpage", "acquaintances", "educ_club", "educ_team", "migrant_club", "migrant_team", "chosen")]
    
    if(set == 1 & choice == 1) {
      df_long <- data
    } else {
      df_long <- rbind(df_long, data)
    }
  }
}

# reorder
df_long <- df_long[order(df_long$id, df_long$set, df_long$options), ]

# define the choice
df_long$choice <- (df_long$chosen == c(1, 2)[df_long$options])

# recode numeric levels, and make of class factor
df_long <- df_long %>% mutate(
  
  traveltime = case_when(
    traveltime == 1 ~ "travel time: 5 minutes",
    traveltime == 2 ~ "travel time: 15 minutes",
    traveltime == 3 ~ "travel time: 30 minutes"),
  
  trainfreq = case_when(
    trainfreq == 1 ~ "training frequency: once a week",
    trainfreq == 2 ~ "training frequency: more than once a week"),
  
  webpage = case_when(
    webpage == 1 ~ "webpage statement: 'exercising together is building friendships!'",
    webpage == 2 ~ "webpage statement: 'lift yourself to a higher level!'"),
  
  acquaintances = case_when(
    acquaintances == 1 ~ "acquaintances: multiple",
    acquaintances == 2 ~ "acquaintances: none"),
    
  educ_club = case_when(
    educ_club == 1 ~ "club members with tertiary education: a quarter (25%)",
    educ_club == 2 ~ "club members with tertiary education: half (50%)",
    educ_club == 3 ~ "club members with tertiary education: three quarters (75%)"),
  
  migrant_club = case_when(
    migrant_club == 1 ~ "club members with migration background: a few (5%)",
    migrant_club == 2 ~ "club members with migration background: minority (10%)",
    migrant_club == 3 ~ "club members with migration background: a quarter (25%)"),
    
  educ_team = case_when(
    educ_team == 1 ~ "contacts with tertiary education: minority (10%)",
    educ_team == 2 ~ "contacts with tertiary education: a quarter (25%)",
    educ_team == 3 ~ "contacts with tertiary education: half (50%)",
    educ_team == 4 ~ "contacts with tertiary education: three quarters (75%)",
    educ_team == 5 ~ "contacts with tertiary education: majority (90%)"),
    
  migrant_team = case_when(
    migrant_team == 1 ~ "contacts with migration background: none (0%)",
    migrant_team == 2 ~ "contacts with migration background: a few (5%)",
    migrant_team == 3 ~ "contacts with migration background: minority (10%)",
    migrant_team == 4 ~ "contacts with migration background: a quarter (25%)",      
    migrant_team == 5 ~ "contacts with migration background: half (50%)")
  )

row.names(df_long) <- 1:nrow(df_long)

#remove "chosen" and "options"
names(df_long)
df_long <- df_long[, -c(3, 12)]

#last, reorder attribute levels
df_long$traveltime <- factor(df_long$traveltime, levels = c("travel time: 5 minutes", "travel time: 15 minutes", "travel time: 30 minutes"))
df_long$trainfreq <- factor(df_long$trainfreq, levels = c("training frequency: once a week", "training frequency: more than once a week"))
df_long$webpage <- factor(df_long$webpage, levels = c("webpage statement: 'exercising together is building friendships!'", "webpage statement: 'lift yourself to a higher level!'"))
df_long$acquaintances <- factor(df_long$acquaintances, levels = c("acquaintances: none", "acquaintances: multiple"))
df_long$educ_club <- factor(df_long$educ_club, levels = c("club members with tertiary education: a quarter (25%)", "club members with tertiary education: half (50%)", "club members with tertiary education: three quarters (75%)"))
df_long$migrant_club <- factor(df_long$migrant_club, levels = c("club members with migration background: a few (5%)", "club members with migration background: minority (10%)", "club members with migration background: a quarter (25%)"))
df_long$educ_team <- factor(df_long$educ_team, levels = c("contacts with tertiary education: minority (10%)", "contacts with tertiary education: a quarter (25%)", "contacts with tertiary education: half (50%)", "contacts with tertiary education: three quarters (75%)", "contacts with tertiary education: majority (90%)"))
df_long$migrant_team <- factor(df_long$migrant_team, levels = c("contacts with migration background: none (0%)", "contacts with migration background: a few (5%)", "contacts with migration background: minority (10%)", "contacts with migration background: a quarter (25%)", "contacts with migration background: half (50%)"))
``` 

<br>

# save data
```{r, save, eval=FALSE}
fsave(df_long, "conjoint.Rda")
```

<br>

The resulting data-object can be obtained by downloading: `r xfun::embed_file("./data_shared/conjoint.RDa")`
